\documentclass[a4paper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{ngerman} % german language support
\usepackage{../standard}

\title{Faction Notes}
\author{Alden Davidson}

\begin{document}
\maketitle
\tableofcontents

\begin{abstract}
  Sources for this writeup include the official
  \href{https://5e.tools/adventure.html#cos}{Curse of Strahd Gamemaster's Manual} and
  \href{https://www.reddit.com/r/CurseofStrahd/comments/9bpzbh/curse_of_strahd_reloaded_compilation_thread/}{Curse of Strahd: Reloaded}.
  
  This template is built from the
  \href{https://slyflourish.com/rotldm_template.html}{Lazy Dungeon Master Adventure Prep Template} by
  \href{https://slyflourish.com/about_mike_shea.html}{Mike Shea} of \href{https://slyflourish.com/}{Sly Flourish}.
\end{abstract}

\pagebreak
\section{Bildrath Cantemir}
\begin{itemize}
  \item Bildrath offered a 20gp discount on a single purchase if the Party retrieves a lost package downstream of
  the Ivlis River Bridge.
\end{itemize}

\section{Druids of Yester Hill}
\begin{itemize}
  \item The Druids are not yet aware of the events at the Wizard of Wines, but will in due time if the Party does 
  not deal with them beforehand.
\end{itemize}

\section{Gunther and Yelena Arasek}
\begin{itemize}
  \item Gunther purchased a dream pastry from the party, not realizing that it is highly addictive. However, the 
  Party refunded him for the ``bad'' pastry and the Arasek's bear no ill-will towards them anymore.
\end{itemize}

\section{Ireena Kolyana}
\begin{itemize}
  \item Ireena is very grateful to the party for safely escorting her to Vallaki (with minimal detours).
  \item Ireena has become very close with Lord Vasili von Holtz, not suspecting his true identity due to his 
  charm.
  \item The Party is unaware that Ireena has been bitten twice by Strahd von Zarovich, and Ireena guards this
  secret very closely; she often wears a scarf to hide the mark.
  \item Ireena has been kidnapped by Izek Strazni and is locked in his rooms in the Baron's mansion.
\end{itemize}

\section{Ismark Kolyana}
\begin{itemize}
  \item Ismark was skeptical that the party weren't vagabonds or evildoers, due to what they did to his village's 
  church and Father Donavich. They have earned his trust by successfully escorting his sister Ireena to Vallaki 
  and returning with proof that the task was completed satisfactorily.
  \item Ismark was further impressed by the party when they returned the ``abducted'' children from Old 
  Bonegrinder and unveiled the true nature of Morgantha and the coven.
\end{itemize}

\section{Keepers of the Feather}
\begin{itemize}
  \item The Keepers of the Feather believed that the party was evil, likely servants of Strahd, due to Muriel's 
  report of the party ransacking the church in Barovia and terrorizing Father Donavich.
  \item Since the Party successfully saved the Wizard of Wines from its druidic occupation, Urwin is willing to 
  trust the Party with further missions if necessary. However, he still is wary of them given his first impression 
  of them and views them as unhinged and unpredictable.
\end{itemize}

\section{Madam Eva}
\begin{itemize}
  \item Madam Eva has told the fortunes of the party and its constituent members.
\end{itemize}

\section{Morgantha's Coven}
\begin{itemize}
  \item The coven was broken when the party slew the two ``sisters'' at Old Bonegrinder. Morgantha is aware of 
  their deaths but unaware precisely who is behind it. She will be focused exclusively on determining who 
  perpetrated this agression against the coven and then will try to haunt them relentlessly.
\end{itemize}

\section{Rictavio}
\begin{itemize}
  \item The party suspects that he is more than what he claims (a traveling bard) due to the armored tiger in his 
  wagon.
  \item Rictavio is willing to trust the Party, since they have chosen to help him skip town following the Mayor's
  discovery of his ownership of the tiger.
\end{itemize}

\section{Strahd von Zarovich}
\begin{itemize}
  \item Strahd is aware that the party destroyed Death House permanently since they buried Walter's corpse and 
  thus released his soul and the curse on the house.
  \item Strahd is aware that one of the party somehow met an Evil Vestige. Strahd doesn't know this, but the 
  Vestige was Norganas, Finger of Oblivion; Norganas was able to communicate due to Death House amplifying his 
  power.
  \item Strahd has met the party personally as Lord Vasili von Holtz. He is also aware that Ireena is in Vallaki 
  now, and will start trying to charm her whenever he has a chance.
\end{itemize}

\section{Vargas Vallakovich}
\begin{itemize}
  \item He was impressed by the Party's dutiful escorting of Ireena into his care and invited them to be his
  honored guests at the Festival of the Burning Sun on 27 Oct.
  \item The Baron tolerates Ireena's imprisonment since he views Ireena as a potential pawn to gaining control over 
  the village of Barovia. He is unaware that Strahd also covets her.
  \item The Baron will be furious at the Party aiding Rictavio to escape Vallaki, and will ban them from entering
  the town.
\end{itemize}

\end{document}
