\pagebreak
\section*{Aftermath of Escape}
\addcontentsline{toc}{section}{Aftermath of Escape}
\label{sec:AftermathOfEscape}
Once all PCs have either escaped from or been trapped by the house:
\begin{readout}
  As you stumble out of the house and race to the edge of the road, you turn to look back at whence you came.
  The house is crumbling and sagging in on itself, groaning mournfully and almost angrily, yet definitely still 
  standing; it reminds you of a fighter in a tough boxing match, bruised and bloodied yet defiant.
\end{readout}
If you choose to use the \textbf{Walter, the Flesh Mound} encounter, Death House will reset (and, if destroyed,
reform) soon after the PCs leave it, once more awaiting new travellers that it can ensnare. The only way to
remove its curse permanently is to remove Walter's body from the remnants of the Mound below, and to bury it
at the threshold of the House outside. If the PCs bury Walter:
\begin{readout}
  As you bury Walter and step back to examine your work, the ground begins to shudder and the whole house
  almost seems to convulse. Slowly, as if some evil is trying to fight back, the house collapses in on itself
  and is swallowed up in the ground. Only the two outbuildings -- the stable and the servants' house -- remain 
  as a sign of what was once in the grassy meadow before you.
\end{readout}

\subsubsection*{Norganus, the Finger of Oblivion}
If any PCs were trapped inside Death House, Norganus, the Finger of Oblivion appears to you as if in a dream.
\begin{readout}
  The last thing you recall is being about to escape, yet suddenly you find yourself being dragged back in 
  through the front doors of the house you've been exploring, your legs and ankles seized by shrieking spirits 
  and hissing ghouls; inside, the house has become a craggy fissure in the ground -- both fiery and pitch-black 
  at the same time.
  
  Just before you cross the threshold a tall, dark, human-shaped shadow with indistinguishable features appears 
  before you and time seems to slow to a standstill. The shadow holds out its hand -- an inky black void dripping 
  a foul, ichorous ooze from its fingertips -- and in a soft, hissing voice whispers, ``Such wasted potential, it 
  would be a grave disservice to the world and those that care for you to see it lost so soon. Take my hand, and 
  I will free you from these `unquiet dead'{}'', and he gestures to the spirits and ghouls holding your legs and 
  ankles.
\end{readout}
If the PCs take his hand and accept Norganus' dark gift, they awaken in the tall grass in front of the house. PCs
that have been resurrected this way gain the \textit{Touched by the Mists} trait, which leaves them tainted by
Norganus' evil touch. Cats hiss and milk sours at their approach, and they detect as evil-aligned undead to
divination magic. These traits remain until the PC receives a \textit{remove curse} spell. Moreover, any such PCs
marked by Norganus specifically gain one of the following Dark Gifts:
\begin{itemize}
  \item The characters's eyes melt away, leaving empty sockets. He/she has disadvantage on Charisma (Persuasion) 
  checks, but gains blindsight out to a range of 60 feet. The character is blind beyond this distance.
  \item The character's skin is cold and clammy to the touch. The character gains resistance to cold damage and
  vulnerability to fire damage.
  \item At night, the character can spend 1 hit die to move through solid objects as though they were difficult
  terrain. A character who ends his or her turn inside an object takes 5 (1d10) force damage. The character
  counts as an undead creature for the purpose of spells and effects such as turn undead.
\end{itemize}

\subsubsection*{Welcome to Barovia}
Regardless of the ultimate outcome of the ritual, Strahd is aware of the events beneath Death House and may taunt
the PCs for their decisions in the dungeon below.
\begin{readout}
  As you turn back to the road to continue heading west, you notice a sign pointing in the wrong direction that
  reads: ``Death House -- Don't talk to the Children!''. Beside it is a small wooden box.
\end{readout}
If the PCs open the box:
\begin{readout}
  Inside the box are \textit{<X>} health potions \{\textit{If PCs buried Walter:} and a bottle labeled ``Purple 
  Dragon Crush''\}. It also contains a letter with a wax seal bearing a crest you've seen before.
\end{readout}
\textit{X} is the number of players that successfully escaped Death House. The crest is Strahd's.

If the PCs didn't bury Walter -- and thus actually destroy the house and cult for good, a ``slow clap'' sound 
effect plays when the letter is opened.
\begin{handout}
  Thank you for cleaning this vermin off of my domain. Your efforts are appreciated, even if for just one night.
  
  Please accept this small gift to help your recovery.
  
  Welcome to Barovia. -S
\end{handout}
Otherwise, the letter simply reads:
\begin{handout}
  Thank you for cleaning this vermin off of my domain; your thorough efforts are much appreciated.
  
  Please accept this small gift to help your recovery.
  
  Welcome to Barovia. -S
\end{handout}
