\documentclass[a4paper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{ngerman} % german language support
\usepackage{../gmnotes}


\title{Death House}
\author{Alden Davidson}

\begin{document}

\maketitle
\tableofcontents

\begin{abstract}
Sources for this writeup include the official Curse of Strahd Gamesmaster's Manual and Curse of Strahd: Reloaded.
\end{abstract}

\pagebreak
\section*{Approaching Death House}
\addcontentsline{toc}{section}{Approaching Death House}
\label{sec:ApproachingDeathHouse}
\begin{readout}
As you continue up the road, dark storm clouds quickly begin to gather and before long a vicious thunderstorm has 
erupted; the wind is whipping violently, the rain is heavy like it's trying to pound you into the ground beneath 
you, and the flashes of lightning are often a bit too close for comfort.

In the distance farther down the road, you see a light in the darkness. As you approach it, you can begin making 
out more detail -- the light is a lantern held by a girl, probably a bit younger than teenage, and a boy a few 
years younger still. They are both standing beneath the awning over the front door of an old house, where the 
girl appears to be sheltering the boy from the rain and waving to you as if trying to signal for help.
The boy is holding a stuffed doll fearfully. The house is flanked by two sad-looking structures;
one appears to be a servants' house and the other a stable.
\end{readout}

\begin{arealinks}
  \item \nameref{sec:InsideDeathHouse}
\end{arealinks}


\pagebreak
\section*{Inside Death House}
\addcontentsline{toc}{section}{Inside Death House}
\label{sec:InsideDeathHouse}

\input{floor01}
\input{floor02}
\input{floor03}
\input{floor04}
\input{dungeon}
\input{skillchallenge}


\pagebreak
\section*{Aftermath of Escape}
\addcontentsline{toc}{section}{Aftermath of Escape}
\label{sec:AftermathOfEscape}
If any PCs were trapped inside Death House, Norganus, the Finger of Oblivion appears to you as if in a dream.
\begin{readout}
  Suddenly, you find yourself dragged through the front doors of the house you've been exploring, your legs and 
  ankles seized by shrieking spirits and hissing ghouls. Just before you cross the threshold a tall, dark, human-
  shaped shadow with indistinguishable features appears before you and time seems to slow to a standstill.
  The shadow holds out its hand -- an inky black void dripping a foul, ichorous ooze from its fingertips -- and 
  in a soft, hissing voice whispers, ``Such wasted potential, it would be a grave loss to the world and those 
  that care for you to see it lost so soon. Take my hand, and I will free you from these `unquiet dead'{}'', and 
  he gestures to the spirits and ghouls holding your legs and ankles.
\end{readout}
If the PCs take his hand and accept Norganus' dark gift, they awaken in the tall grass in front of the house. PCs
that have been resurrected this way gain the \textit{Touched by the Mists} trait, which leaves them tainted by
Norganus' evil touch. Cats hiss and milk sours at their approach, and they detect as evil-aligned undead to
divination magic. These traits remain until the PC receives a \textit{remove curse} spell. Moreover, any such PCs
marked by Norganus specifically gain one of the following Dark Gifts:
\begin{itemize}
  \item The characters's eyes melt away, leaving empty sockets. He/she has disadvantage on Charisma (Persuasion) 
  checks, but gains blindsight out to a range of 60 feet. The character is blind beyond this distance.
  \item The character's skin is cold and clammy to the touch. The character gains resistance to cold damage and
  vulnerability to fire damage.
  \item At night, the character can spend 1 hit die to move through solid objects as though they were difficult
  terrain. A character who ends his or her turn inside an object takes 5 (1d10) force damage. The character
  counts as an undead creature for the purpose of spells and effects such as turn undead.
\end{itemize}
Regardless of the ultimate outcome of the ritual, Strahd is aware of the events beneath Death House and may taunt
the PCs for their decisions in the dungeon below.

If you choose to use the \textbf{Walter, the Flesh Mound} encounter, Death House will reset (and, if destroyed,
reform) soon after the PCs leave it, once more awaiting new travellers that it can ensnare. The only way to
remove its curse permanently is to remove Walter's body from the remnants of the Mound below, and to bury it
at the threshold of the House outside.


\pagebreak
\subsection*{Resting Inside Death House}
\addcontentsline{toc}{section}{Resting Inside Death House}
\label{sec:RestingInsideDeathHouse}
If the PCs take a long rest in this or any other room of Death House, roll to randomly select a PC to have
a nightmare while resting. This PC will receive a level of exhaustion upon waking. Use one or all of the
following haunts while the PCs sleep:
\begin{itemize}
  \item A PC hears rats scrabbling up and down the spaces between the walls.
  \item A PC hears footsteps descending from the attic and stopping outside of their door before moving away
  to the library. Soon after, a grinding noise can be heard coming from the library (the sound of a secret door).
  \item A PC hears maniacal laughter echoing from far below the House.
  \item A PC experiences a false awakening, wherein they wake to see that one of their friends has been replaced
  by a ghast, which is slowly creeping towards another PC. If the PC stays still, the ghast slices open its
  victim's throat and the PC watches their friend bleed out before waking up.
  \item A PC overhears a whispered argument about parentage. A pleading female voice in the PC's right ear
  swears that ``it isn't his''. A cold female voice in the PC's left ear scoffs, and says that it doesn't care.
\end{itemize}
If the PCs damage anything on the first or second floor in their search for traps or treasure and return to
any such chambers after a long rest, let them know that the rooms have been restored to pristine condition.

\end{document}
