\pagebreak
\subsection{Upper Hall}
\label{sec:UpperHall}
\begin{readout}
  Unlit oil lamps are mounted on the walls of this elegant hall. Standing suits of armor flank wooden doors in
  the east and west walls. Each suit of armor clutches a spear and has a visored helm shaped like a wolf's head.
  The doors are carved with dancing youths. \{\textit{PCs with 12+ passive perception:} Closer inspection
  reveals that the youths aren't really dancing but fighting off swarms of bats.\} The red marble staircase that
  started on the first floor continues its upward spiral. A cold draft can be felt coming down the steps.
  
  Hanging above the mantelpiece is a wood-framed portrait of a family: a man and woman with two smiling
  children, and a swaddled baby in the father's arms that the mother regards with a hint of scorn. You
  recognize the mother and father from the portraits in the foyer downstairs; more unsettlingly, you also
  recognize the two children - they're the boy and girl that asked you for help at the entrance of the house!
\end{readout}

A PC that listens at the door of the Servants' Room can smell blood, and hear the sobs and muffled gasps of a
woman in pain.

\begin{arealinks}
  \arealink{sec:MainHall}
  \arealink{sec:ServantsRoom}
  \arealink{sec:Library}
  \arealink{sec:Conservatory}
  \arealink{sec:Balcony}
\end{arealinks}

\pagebreak
\subsection{Servants' Room}
\label{sec:ServantsRoom}
\begin{readout}
  An undecorated bedroom contains a pair of beds with straw-stuffed mattresses. At the foot of each bed is
  an empty footlocker. In the southwest corner there is a very small, 2-foot-wide door set in the wall 
  at waist height with a button next to it.
\end{readout}
When PCs enter Area 7B:
\begin{readout}
  It's a closet. Tidy servants' uniforms hang from hooks.
\end{readout}

\subsubsection*{Dumbwaiter}
The shaft connects to the servants' quarters (Area 7A) and the master bedroom (Area 12A). A small character can
squeeze into the elevator box with a successful DC 10 Dexterity (Acrobatics) check. The dumbwaiter's
rope-and-pulley mechanism can support 200 pounds of weight before breaking. Pressing the button rings the tiny
bell in the kitchen (Area 4A), which can be faintly heard from this room.

\begin{arealinks}
  \arealink{sec:KitchenAndPantry}
  \arealink{sec:UpperHall}
  \arealink{sec:MasterSuite}
\end{arealinks}


\pagebreak
\subsection{Library}
\label{sec:Library}
\begin{readout}
  Red velvet drapes cover the windows of this room. An exquisite mahogany desk and a matching high-back chair
  face the entrance and the fireplace, above which hangs a framed picture of a windmill perched atop a rocky
  crag. Situated in corners of the room are two overstuffed chairs. Floor-to-ceiling bookshelves line the south
  wall and contain hundreds of tomes covering a range of topics including history, warfare, and alchemy as well
  as several first-edition collected works of poetry and fiction. A rolling wooden ladder allows one to more
  easily reach the high shelves. \{\textit{PCs with 15+ passive perception:} You can see flickering candlelight
  beneath the bookshelf in the southeast corner.\}
\end{readout}
When a PC searches the desk:
\begin{readout}
  The desk has several items resting atop it: an oil lamp, a jar of ink,
  a quill pen, a tinderbox, and a letter kit containing a red wax candle, four blank sheets of parchment, and
  a wooden seal bearing the same windmill insignia you've seen around the house. One desk drawer is empty except
  for an iron key. Another drawer has a tattered piece of sheet music in it, titled ``Song for Elisabeth'' as
  well as a handwritten, partially burnt note that reads ``Bulwarton's words can open the way''. Finally, a
  third drawer contains a number of receipts for candles, daggers, and incense.
\end{readout}
The iron key unlocks the door to the children's room (Area 20).

A red-covered book with a black spine titled ``An Architect's Art'' by Archibald Bulwarton is fake and opens
the secret door. All the books rot and fall apart if taken from the house.

\subsubsection*{Spooky Autobiography}
Roll to select a random PC for this minor encounter.
\begin{readout}
  One of the books on the shelves is titled ``The History of [\textit{PC's Name}]''.
  \textit{If the PC reads it:} It provides a narration of your entire life. The final page has a large
  bloodstain on it and reads: ``[He/She/They] pulled the book down off the shelf and began to read, unaware
  of the creature that watched [him/her/them] from the shadows. Slowly, the beast began to creep forward.''
\end{readout}
A search of the room evidences no indication of any other creature (besides your party members, if present).

\subsubsection*{Secret Door}
A secret door behind one bookshelf can be unlocked and swung open by pulling on a switch disguised to look like
a red-covered book with a black spine. A character inspecting the bookshelf spots the fake book with a successful
DC 13 Wisdom (Perception) check. Unless the secret door is propped open, springs in the hinges cause it to
close on its own. Beyond the secret door lies the secret room (Area 9).

\begin{arealinks}
  \arealink{sec:UpperHall}
  \arealink{sec:SecretRoom}
\end{arealinks}


\pagebreak
\subsection{Secret Room}
\label{sec:SecretRoom}
\begin{readout}
  This secret room contains bookshelves packed with tomes describing fiendsummoning incantations and the
  necromantic rituals of a cult called the Priests of Osybus. A heavy wooden chest with clawed iron feet
  stands against the south wall, its lid half-closed. Sticking out of the chest is a skeleton in leather
  armor. Close inspection reveals that the skeleton belongs to a human who triggered a poisoned dart trap.
  Three darts are stuck in the dead adventurer's armor and ribcage. There is a letter clutched in the
  skeleton's left hand.
\end{readout}
The rituals described in the books are bogus, which any PC can ascertain after studying the books for 1 hour
and succeeding on a DC 12 Intelligence (Arcana) check.

The dart-firing mechanism inside the chest no longer functions. The letter in the skeleton's hand bears the
seal of Strahd von Zarovich, which the adventurer tried to remove from the chest. Written in flowing script,
the letter reads as follows:
\begin{handout}
  My most pathetic servant,
  
  I am not a messiah sent to you by the Dark Powers of this land. I have not come to lead you on a path of
  immortality. However many souls you have bled on your hidden altar, however many visitors you have tortured
  in your dungeon, know that you are not the ones who brought me to this beautiful land. You are but worms
  writhing in my earth.
  
  You say that you are cursed, your fortunes spent. You abandoned love for madness, took solace in the bosom
  of another woman, and sired a bastard son. Cursed by darkness? Of that I have no doubt. Save you from your
  wretchedness? I think not. I much prefer you as you are.
  
  Your dread lord and master,
  
  Strahd von Zarovich.
\end{handout}

\subsubsection*{Treasure}
\begin{readout}
  The chest contains three blank books with black leather covers (worth 25 gp each), three spell scrolls,
  the deed to the house you are in, the deed to a windmill, and a signed will. The windmill referred to in
  the second deed is situated in ``the mountains east of Vallaki''. The will is signed by Gustav and Elisabeth
  Durst, and bequeaths the house, the windmill, and all other family property to Rosavalda and Thornboldt Durst
  in the event of their parents' deaths. Tucked away in the alcove alongside the deed to the windmill is
  a letter addressed to one ``Dimov''.
\end{readout}
The books, scrolls, deeds, and will age markedly if taken from the house but remain intact.
\begin{handout}
  My dear Dimov,
  
  I must confess, my nights as of late have been sleepless. The child's wails these past several evenings
  have kept me awake, haunting these halls like a ghost. Margaret does her best, but other clouds yet trouble
  my dreams.
  
  My beloved Elisabeth, I am sure, feels it too, for she tosses and turns in our bed and awakes with her
  forehead slick with sweat. O'er the past several congregations, I have become suspicious of the ambitions
  of the others. Their dark murmurs worry me and, though I know that a shadow ought not fear a blacker night,
  I cannot but fear for the extent of their plotting.
  
  If anything happens, you are to be steward of our parents' house, and caretaker of my children. Keep Rose
  and Thorn safe, and dear Walter close to your breast. Should the worst come to pass, you shall be all they
  have left.
  
  Your loving brother,
  
  Gustav
\end{handout}

\begin{arealinks}
  \arealink{sec:Library}
\end{arealinks}


\pagebreak
\subsection{Conservatory}
\label{sec:Conservatory}
\begin{readout}
  Gossamer drapes cover the windows of this elegantly appointed hall, which has a brass-plated chandelier
  hanging from the ceiling. Upholstered chairs line the walls, and stained-glass wall hangings depict beautiful
  men, women, and children singing and playing instruments.
  
  A harpsichord with a bench rests in the northwest corner. Near the fireplace is a large standing harp.
  Alabaster figurines of well-dressed dancers adorn the mantelpiece. Close inspection of them reveals that
  several are carvings of well-dressed skeletons.
\end{readout}

If a PC plays the ``Song for Elisabeth'' found in the library desk on the harpsichord:
\begin{readout}
  The conservatory fills with ghosts that dance about the room to the tune of the melody. The ghosts take no
  notice of you all, save for two: a man and a woman that you recognize from the pictures around the house,
  \{\textit{If the PCs have found the secret room (Area 9)} presumably the Gustav and Elisabeth Durst mentioned
  in the documents you found earlier,\} who stand beside the fireplace, staring at you. As soon as you notice
  them, the harpsichord's strings are cut, the ghosts vanish, and a grinding sound like stone on stone can be
  heard from above.
\end{readout}

If a PC searches the room or at another opportune moment before the PCs leave:
\begin{readout}
  You find a small dog hiding under an armchair. He is rail-thin and clearly starving, and seems to be
  terrified of anyone that approaches him. 
\end{readout}
The dog has a tag on his leash that identifies him as Lancelot, owned by Gertruda; this can be seen once he is
coaxed out. As Mad Mary lost herself to grief, Lancelot left his house in order to search for Gertruda. He
wandered into Death House, and was trapped in the conservatory when the house shut the door behind him. He
can be coaxed out from his hiding spot, however, with a DC 10 Wisdom (Animal Handling) check, with advantage
if offered food.

The cult of Death House consideres Lancelot an acceptable sacrifice if killed on the altar.

If the PCs exit the room without playing the harpsichord:
\begin{readout}
  You hear the sound of a harpsichord playing faintly from the room you just left.
  \{\textit{If the PCs have the sheet music for ``Song for Elisabeth'':} You recognize it as the
  ``Song of Elisabeth'' that you have sheet music for from the library.
\end{readout}
The music continues to play until the room is re-entered.

\begin{arealinks}
  \arealink{sec:UpperHall}
\end{arealinks}
