\subsection{Entrance}
\label{sec:Entrance}
\begin{readout}
  A wrought-iron gate with hinges on one side and a lock on the other fills the archway of a stone portico.
  The gate is unlocked, and its rusty hinges shriek when the gate is opened. Oil lamps hang from the portico
  ceiling by chains, flanking a set of oaken doors that open into a foyer.
  
  Hanging on the south wall of the foyer is a shield emblazoned with a coat-of-arms, flanked by framed portraits 
  of stony-faced aristocrats. The coat-of-arms is a stylized golden windmill on a red field. Mahogany-framed 
  double doors set with panes of stained glass lead further into the house.
\end{readout}
The portraits are of the long-dead members of the Durst family.
\begin{arealinks}
  \arealink{sec:MainHall}
\end{arealinks}

\subsubsection*{Skill Challenge Escape: Entrance Foyer}
\label{sec:SC_EntranceFoyer}
\begin{readout}
  To your horror, you discover that the front doors are slowly becoming bricked up -- and behind them, the doors 
  to the Main Hall begin to swing shut.
\end{readout}
Characters can make a DC 12 Dexterity saving throw to hurl themselves into the Main Hall before the doors swing 
shut. Otherwise, read the following:
\begin{readout}
  The mahogany hall doors behind you slam shut with ominous thunder. You look about the room, desparate to escape
  -- and when you look toward the exit, you see the bottom third of the front door has been replaced by brick.
  Defying all logic, the wood has melded into the rows of moldy brick. You blink -- and to your mounting horror,
  in that span of a second, more of the door has been converted. You keep your eyes wide open so as to not cast
  away your chance at breaking down the door, but that's when a fetid cloud of filth rolls in, stinging your
  eyes and drawing tears. The walls are brittle now, rotton. The wallpaper hangs in slivers, and from behind
  the plaster a flood of rats bursts onto the floor, crawling across your feet and scratching at your flesh.
\end{readout}
A PC that attempts a skill check in this room must succeed on a DC 10 Constitution saving throw, or the rats'
stench causes them to falter giving them disadvantage on their check.
\begin{skillChallenge}
  \begin{itemize}
    \item \textbf{Athletics} or combat \textbf{spells} can be used to break through the rotton, brittle walls
    \easyDC; the bricked-up front door \hardDC; or the stuck hallway doors \moderateDC.
    \item \textbf{Nature}, \textbf{Intimidation}, or \textbf{Animal Handling} can be used to keep the rats away.
    \moderateDC
    \item \textbf{Perception} or \textbf{Investigation} can allow a PC to see a point in the bricks where they
    have become weak and crumbling. \moderateDC
  \end{itemize}
\end{skillChallenge}

\subsubsection*{Skill Challenge Escape: Entrance Gate}
\label{sec:SC_EntranceGate}
This challenge takes place only if one or more of the PCs are still possessed by the spirits of Rose and Thorn.
As the PCs approach the iron gate, the ghosts struggle with the PCs for control of their bodies, and beg and
plead for the PCs to stay behind.
\begin{skillChallenge}
  \begin{itemize}
    \item \textbf{Athletics} can be used by an unpossessed character to force a possessed PC over the threshold.
    The possessed PC must succeed on a DC 10 Wisdom saving throw or take 1d4 psychic damage as the spirit is
    violently torn from their body. \hardDC
    \item \textbf{Persuasion} or \textbf{Intimidation} can be used to coax the spirits from their unwilling
    hosts. \easyDC
    \item \textbf{Arcana} or \textbf{Religion} may allow a character to draw on their reserves of magic or faith,
    respectively, forcefully dispelling the intrusive soul. \moderateDC
  \end{itemize}
\end{skillChallenge}

\begin{arealinks}
  \item \nameref{sec:AftermathOfEscape}
\end{arealinks}


\pagebreak
\subsection{Main Hall}
\label{sec:MainHall}
\begin{readout}
  A wide hall \{\textit{Area 2A}\} runs the width of the house, with a black marble fireplace at one end and
  a sweeping, red marble staircase at the other. Mounted on the wall above the fireplace is a longsword with a
  windmill cameo worked into the hilt. The wood-paneled walls are ornately sculpted with images of vines,
  flowers, nymphs, and satyrs. \{\textit{PCs with 12+ passive perception:} Upon closer inspection, you notice
  that there are serpents and skulls inconspicuously woven into the wall designs.\} The decorative paneling
  follows the staircase as it circles upward to the second floor.
\end{readout}
When the PCs open the door to Area 2B:
\begin{readout}
  The door opens to reveal a cloakroom with several black cloaks hanging from hooks on the wall. A top hat
  sits on a high shelf.
\end{readout}
When a PC listens at the dining room doors, the sound of clinking glass, laughter, and muffled conversation can be heard from beyond. When the door is opened, the PCs find the room to be empty.

\begin{arealinks}
  \arealink{sec:DenOfWolves}
  \arealink{sec:KitchenAndPantry}
  \arealink{sec:DiningRoom}
  \arealink{sec:UpperHall}
\end{arealinks}


\pagebreak
\subsection{Den of Wolves}
\label{sec:DenOfWolves}
\begin{readout}
  This oak-paneled room looks like a hunter's den. Mounted above the fireplace is a stag's head, and positioned
  around the outskirts of the room are three stuffed wolves. Two padded chairs draped in animal furs face the
  hearth, with an oak table between them supporting a cask of wine, two carved wooden goblets, a pipe rack, and
  a candelabrum. A chandelier hangs above a cloth-covered table surrounded by four chairs. Two cabinets stand
  against the walls; the east cabinet sports a lock.
\end{readout}
The stuffed wolves move/adjust their posture when not directly observed.

The east cabinet can be picked with thieves' tools and successful DC 15 Dexterity check. It holds a heavy
crossbow, a light crossbow, a hand crossbow, and 20 bolts for each weapon (for a total of 60 bolts). The north
cabinet is unlocked and holds a small box containing a deck of playing cards and an assortment of wine glasses.

\subsubsection*{Trapdoor}
A trapdoor is hidden in the southwest corner of the floor. It can't be detected or opened until the PCs approach
it from the underside (see Area 32). Until then, Death House supernaturally hides the trapdoor.

\begin{arealinks}
  \arealink{sec:MainHall}
  \arealink{sec:HiddenTrapdoor}
\end{arealinks}

\subsubsection*{Skill Challenge Escape: Den of Wolves}
\label{sec:SC_DenOfWolves}
\begin{readout}
  As you climb out of the trap door, you're greeted by thick clouds of blinding smoke making it impossible to
  see anything past a few feet. You can hear faint snuffing, panting, and growling that sounds like wolves
  pacing around the room, and can see a pair of glowing eyes near you that doesn't seem to have noticed the
  trapdoor being cracked open yet.
\end{readout}
Death House has animated the stuffed wolves in the den and flooded the room with blinding smoke. The wolves have
the statistics of a wolf but with vulnerability to slashing, piercing, and fire damage; their Bite attack deals
1 piercing damage; and they do not need to breathe.
\begin{skillChallenge}
  \begin{itemize}
    \item \textbf{Animal Handling} can be used to subdue the wolves; the long-lost spirits of the beasts still
    obey such primal laws of nature. \moderateDC
    \item \textbf{Stealth} can be used to slip past the wolves undetected. \easyDC
    \item \textbf{Levelled Spells} (Automatic Success) or \textbf{cantrips} \moderateDC such as
    \textit{minor illusion} or \textit{animal friendship} can be used to distract or subdue the wolves.
  \end{itemize}
\end{skillChallenge}


\pagebreak
\subsection{Kitchen and Pantry}
\label{sec:KitchenAndPantry}
\begin{readout}
  The kitchen \{\textit{Area 4A}\} is tidy, with dishware, cookware, and utensils neatly placed on shelves.
  A worktable has a cutting board and rolling pin atop it. A stone, dome-shaped oven stands near the east wall,
  its bent iron stovepipe connecting to a hole in the ceiling. Behind the stove and to the left is a thin door
  \{\textit{Area 4B}\}. In the southwest corner there is a very small, 2-foot-wide door set in the wall 
  at waist height.
\end{readout}
When the PCs enter 4B:
\begin{readout}
  The door opens to a well-stocked pantry. All the food appears fresh.
\end{readout}
The food in the pantry tastes bland.

\subsubsection*{Dumbwaiter}
\begin{readout}
  The small door opens to a 2-foot-wide stone shaft containing a wooden elevator box attached to a simple
  rope-and-pulley mechanism that must be operated manually from the kitchen. Hanging on the wall next to the
  dumbwaiter is a tiny brass bell with two wires running from it into the ceiling.
\end{readout}
The shaft connects to the servants' quarters (Area 7A) and the master bedroom (Area 12A). A small character can
squeeze into the elevator box with a successful DC 10 Dexterity (Acrobatics) check. The dumbwaiter's
rope-and-pulley mechanism can support 200 pounds of weight before breaking.

\begin{arealinks}
  \arealink{sec:MainHall}
  \arealink{sec:ServantsRoom}
  \arealink{sec:MasterSuite}
\end{arealinks}

\subsubsection*{Skill Challenge Escape: Kitchen and Pantry}
\label{sec:SC_KitchenAndPantry}
As a character makes their way in or out of the dumbwaiter, the oven spits a column of fire. Any characters in
the room must make a DC 12 Dexterity saving throw dodge the fire or to clamber into the dumbwaiter, working the 
rope and pulley before being scorched. On a failure, a creature takes 1d6 fire damage but continues upward. The
explosion shakes the entirety of the manor.


\pagebreak
\subsection{Dining Room}
\label{sec:DiningRoom}
\begin{readout}
  The centerpiece of this wood-paneled dining room is a carved mahogany table surrounded by eight high-backed
  chairs with sculpted armrests and cushioned seats. A crystal chandelier hangs above the table, which is
  covered with resplendent silverware and crystalware polished to a dazzling shine, and laid with a magnificent
  feast. Mounted above the marble fireplace is a mahogany-framed painting of an alpine vale.
  
  The wood paneling is carved with elegant images of deer among the trees. \{\textit{PCs with 12+ passive
  perception:} Upon closer inspection, you see twisted faces carved into the tree trunks and wolves lurking 
  amid the carved foliage.\} Red silk drapes cover the windows, and a tapestry depicting hunting dogs and
  horse-mounted aristocrats chasing after a wolf hangs from an iron rod bolted to the south wall.
\end{readout}
A PC that eats any of the food on the table must succeed on a DC 15 Wisdom save, or else be compelled to stuff
themselves with food. After the PC has filled their gullet for a full minute, the glamor upon the banquet
vanishes, revealing it to be rotted, foul meats infested with maggots and stale breads stuffed with weevils.
At this point, the compulsion upon any affected PCs falls, leaving them poisoned for 1 hour.

The silverware tarnishes, the crystal cracks, the portrait fades, and the tapestry rots if removed from the
house.

\begin{arealinks}
  \arealink{sec:MainHall}
\end{arealinks}
