\pagebreak
\section*{Flight from Death House: Skill Challenge}
\addcontentsline{toc}{section}{Flight from Death House: Skill Challenge}
\label{sec:SkillChallenge}
To successfully escape from Death House, the PCs must succeed on a skill challenge. A holdover from 4th edition,
a skill challenge requires the PCs to face a number of obstacles that cannot be solved solely by combat.

Note: the following section is largely copied wholesale from Wyatt Trull's
\href{https://www.dmsguild.com/product/248157/Curse-of-Strahd-Escaping-Death-House-Skill-Challenge}{
\uline{Curse of Strahd: Escaping Death House Skill Challenge}}.

\subsubsection*{Running the Skill Challenge}
Explain to the players that this is a skill challenge, which boils down to the following tenets:
\begin{itemize}
  \item PCs will encounter a series of obstacles that can be solved through their skills and abilities, rather
  than combat.
  \item Only one PC makes an ability check for each obstacle.
  \item The goal of the skill challenge is to reach a hidden number of successful checks.
  \item Skill challenges are about collaborative, creative storytelling. The GM presents the obstacle, and the
  players suggest solutions that utilize their skills. There are almost always multiple ways to overcome an
  obstacle, so don't be afraid to get creative!
  \item Failure on a skill check is not a wall; instead, the PCs progress but at the expense of a resource like
  time, energy, or power.
\end{itemize}
Explain to the players that the skill challenge follows the additional rules:
\begin{itemize}
  \item A skill can be used only once per character (e.g. if Conan the barbarian uses Athletics to leap a chasm,
  he cannot use Athletics again to lift a boulder later. Other PCs, however, can still use Athletics for other
  obstacles.)
  \item Similarly, cantrips can be used once per PC in place of a skill check. The spellcaster must make an
  ability check with their spellcasting ability modifier, adding their proficiency bonus, and comparing it
  against the DC of the obstacle they are facing.
  \item Spells of 1st level or higher are automatic successes, so long as they can be logically used to surpass
  a given obstacle.
  \item Tool checks can be used in lieu of skills if a PC is proficient in them, and if they make sense in the
  context of the given obstacles. (This gives advantage on the skill check.)
  \item There is no set initiative order while running a skill challenge; any PC can seize the initiative when
  faced with a specific obstacle. However, no single PC can take initiative two consecutive obstacles in a row.
\end{itemize}
An \textit{easy} skill check has a DC of 8.
A \textit{moderate} skill check has a DC of 13.
A \textit{hard} skill check has a DC of 18.
These DCs increase by 2 when the PCs reach levels 5, 10, 15, or 20.

Once the challenge begins, swarms of maggots begin to bleed from the walls, floor, and ceiling of any room that
the PCs take refuge in, filling the room completely within 3d4 rounds. Note that only the doorways to Areas 12
and 15 have the scythes mentioned in the module.

Roll initiative upon beginning the skill challenge; on 3 failures, the slowest adventurer is left behind. On
5 failures, the slowest two adventurers are trapped while their companions make it to safety. If the PCs achieve
4 successes before 3 failures, all make it out -- worse for wear, and forced to carry in their hearts this hellish
night forevermore.

\begin{arealinks}
  \arealink{sec:SC_RitualChamber}
\end{arealinks}
