\documentclass[a4paper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{ngerman} % german language support
\usepackage{../lazyNotes}

\title{Barovia - Session 00}
\author{Alden Davidson}

\begin{document}
\maketitle
\tableofcontents

\begin{abstract}
  Sources for this writeup include the official
  \href{https://5e.tools/adventure.html#cos}{Curse of Strahd Gamemaster's Manual} and
  \href{https://www.reddit.com/r/CurseofStrahd/comments/9bpzbh/curse_of_strahd_reloaded_compilation_thread/}{Curse of Strahd: Reloaded}.
  
  This template is built from the
  \href{https://slyflourish.com/rotldm_template.html}{Lazy Dungeon Master Adventure Prep Template} by
  \href{https://slyflourish.com/about_mike_shea.html}{Mike Shea} of \href{https://slyflourish.com/}{Sly Flourish}.
\end{abstract}

\pagebreak
\section{Characters}
\label{sec:Characters}
\subsection{Cinnamon (Carter)}
  Rabbitfolk Artillerist Artificer. Far Traveler. From the Feywild. Tends to run away from problems. Came to
  Barovia to hunt down the werewolves that abducted children from his village.
\subsection{Patrin (Chris)}
  Dragonborn Draconic Bloodline Sorcerer. Solider and Officer. Stubborn. Exiled from his clan for an accidental 
  murder. Needs a mentor and teacher to show him how to use his magic properly. Came to Barovia by (forged)
  invitation of Kolyan Indirovich.
\subsection{Weylan Lawbringer (Justin)}
  Human Paladin. Acolyte. From the city of Solangel. Worships the Protector. Grew up in his father's shadow, and 
  left home to end the source of goblin raids on his city. Came to Barovia to follow a vision from his late 
  father and earn his own glory.
\subsection{Zarus (Greg)}
  Tiefling Barbarian and Undead Warlock. Haunted One. Strong sense of protection for those around him, due to the
  great loss of his family and friends long ago. Avoids entering his rage if possible, since he is addicted to 
  his smelling salts. Has been cursed by Norganus, the Finger of Death. Came to Barovia by (forged) invitation 
  of Kolyan Indirovich.


\pagebreak
\section{Strong Start}
\label{sec:StrongStart}
As the characters enter the village of Barovia, they encounter a raven with blue-tipped wings perched atop one of
the houses flanking the street. This is Muriel, a wereraven, in animal form. She attempts to lead them to the
Blood of the Vine tavern.

\section{Scenes}
\label{sec:Scenes}
\begin{itemize}
  \item The characters hear sobbing, and locate it coming from Mad Mary's Townhouse.
  \item They encounter Arik the Barkeep, and learn of ``mist-touched'' and ``sun-touched'' Barovians.
  \item They encounter Morgantha and her Dream Pastries.
  \item They all have an identical dream leading them to Madam Eva at Tser Pool Encampment.
  \item Mad Mary visits the Mayoral Mansion seeking help finding her daughter from Ismark.
  \item Rahadin delivers a letter for Ireena to the characters (or Ismark/Ireena if present) at the old 
  Burgomaster's burial.
\end{itemize}

\section{Secrets and Clues}
\label{sec:SecretsAndClues}
\begin{itemize}
  \item The leather-bound bundle Bildrath asks for contains explorer's packs he previously sold to another,
  now-dead adventuring party.
  \item The ``mist-touched'' Barovians actually lack a soul entirely. Only Strahd, Madam Eva, the Abbot, the hags
  of Old Bonegrinder, Baba Lysaga, and a select few others know this.
  \item Doru discovered, when released by Strahd, that the wizard's body was nowhere to be found; he is 
  convinced that the mage is not dead.
  \item Many Vistani serve as spies for Strahd, although it is impossible to tell which do or do not.
  \item Donavich: Ireena Kolyana isn't the natural daughter of Kolyan Indirovich. Although Ireena never knew, 
  Kolyan found her at the edge of the Svalich Woods near the Pillarstone of Ravenloft. She was but a girl then 
  and seemed to have no memery of her past. Kolyan adopted her and loved her dearly.
  \item Dream Pastries are made from the ground bones of children; addicted parents sell their own children to 
  buy more, for it is the only escape from the terror of living in Barovia.
  \item Lancelot the dog is the property of Gertruda, the lost daughter of Mad Mary.
  \item Morgantha knows a bit of the Vistani as spies for Strahd and the locations of their camps.
  \item The raven that tries to lead the characters to the tavern is a wereraven named Muriel.
\end{itemize}

\section{Fantastic Locations}
\label{sec:FantasticLocations}
\subsection{E1 - Bildrath's Mercantile}
  Only shop in town. Dark and worn down inside. Items sold at ridiculous markup (10x). Lots of gear looks 
  slightly used.
\subsection{E2 - Blood of the Vine Tavern}
  Village tavern. Owned by three Vistani sisters. Clearly finely appointed in the past, now shoddy.
\subsection{E3 - Mad Mary's Townhouse}
  Two-story townhouse. Owned by Mad Mary. House is disheveled and clearly unkempt for the past week.
\subsection{E4 - Burgomaster's Mansion}
  Small mansion. Gates are twisted and torn, grounds/lawn are very unkempt and clearly heavily-trodden recently.
  Walls are charred and clawed, and all windows are shattered and boarded over. Insides are well-furnished yet
  worn, and there are holy symbols everywhere.
\subsection{E5 - Church}
  Wood and stone church, in need of maintenance and heavily damaged from sources of evil. Mildewy and poorly 
  lit, except in the main chapel area. Scant decorations and poorly appointed rooms.
\subsection{E6 - Cemetery}
  Tightly packed with gravestones more or less worn by time. Enclosed by a wrought iron fence.

\pagebreak
\section{Important NPCs}
\label{sec:ImportantNPCs}
\subsection{Bildrath Cantemir}
  
\subsection{Ismark Kolyana}
\subsection{Mad Mary}
\subsection{Ireena Kolyana}
\subsection{Donavich}
\subsection{Doru}
\subsection{Morgantha}

\pagebreak
\section{Potential Monsters}
\label{sec:PotentialMonsters}

\pagebreak
\section{Potential Treasure}
\label{sec:PotentialTreasure}

\end{document}
